Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2025-03-10 main.tex
minor fix

We also report in  Figure~\ref{fig:ms-relations-by-workflow} the relative makespan found
by the memory-aware heuristics, normalized to the
makespan achieved by \heft, \new{the latter} often with an invalid over-optimistic schedule that exceeds
the memory bound.
%    Figure~\ref{fig:ms-relations-by-workflow} shows the relations of the makespans found by the heuristics to the
%    makespans found by the baseline (including invalid ones), by workflow size.
\new{The makespans found by \heftbl are $<13\%$ worse than those found by the baseline for workflows with less than \numprint{2000}
tasks, and up to $27\%$ worse for the largest workflows.
The makespans of \heftblc are very similar, being $<17\%$ worse on smallest workflows, $19$-$28\%$ worse on middle-sized,
and up to $30\%$ worse on the largest workflows.
The makespans found by \heftmm are $25$-$30\%$ worse on the smallest workflows, $40$-$70\%$ on middle-sized and up to
$210\%$ on the largest ones.} These are still very encouraging results,
in particular for \heftbl and \heftblc, since the makespans of \heft\ \new{often} correspond to invalid schedules.

>>>>

We also report in  Figure~\ref{fig:ms-relations-by-workflow} the relative makespan found
by the memory-aware heuristics, normalized to the
makespan achieved by \heft, \new{the latter} often with an invalid over-optimistic schedule that exceeds
the memory bound.
%    Figure~\ref{fig:ms-relations-by-workflow} shows the relations of the makespans found by the heuristics to the
%    makespans found by the baseline (including invalid ones), by workflow size.
\new{The makespans found by \heftbl are $<13\%$ worse than those found by the baseline for workflows with less than \numprint{2000}
tasks, and up to $27\%$ worse for the largest workflows.
The makespans of \heftblc are very similar, being $<17\%$ worse on smallest workflows, $19$-$28\%$ worse on middle-sized,
and up to $30\%$ worse on the largest workflows.
The makespans found by \heftmm are $25$-$30\%$ worse on the smallest workflows, $40$-$70\%$ on middle-sized and up to
$210\%$ on the largest ones.} These are still very encouraging results,
in particular for \heftbl and \heftblc, since the makespans of \heft\ \new{nearly always} correspond to invalid schedules.
